SunPy - Python for Solar Physics

### 2014-01-29 2-1-Map.tex
repaired i.e. and e.g.

The \texttt{Map} class stores standard metadata retrieved from the header of 
the image file in the \texttt{meta} attribute and provides convenience 
properties for commonly accessed metadata: \textit{e.g.}, \texttt{instrument}, 
\texttt{wavelength} or \texttt{coordinate\_system}. 
Listing \ref{code:aia_1} demonstrates the quick-look functionality of 
\texttt{Map}; see Section \ref{subsec:Viz} for more discussion of plotting.

>>>>

The \texttt{Map} class stores standard metadata retrieved from the header of 
the image file in the \texttt{meta} attribute and provides convenience 
properties for commonly accessed metadata: e.g., \texttt{instrument}, 
\texttt{wavelength} or \texttt{coordinate\_system}. 
Listing \ref{code:aia_1} demonstrates the quick-look functionality of 
\texttt{Map}; see Section \ref{subsec:Viz} for more discussion of plotting.

### 2014-01-29 2-Data_Types.tex
repaired i.e. and e.g.

These classes allow access to the original data
along with associated metadata and provide appropriate convenience functions to
enable data analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute while the metadata is stored 
in the \texttt{meta} attribute. (Curently, \texttt{LightCurve} does 
not support the \texttt{meta} attribute.) It is possible to instantiate the
data types from various
different sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order 
to provide instrument-specific specialisation, all the core SunPy data types 
support subclassing; \textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the SDO/AIA instrument. 
Data visualisation is provided by two functions: \texttt{peek()}, for quick 
plotting, and \texttt{plot()}, for plotting with more fine-grained control that 
integrates with \texttt{matplotlib}.

>>>>

These classes allow access to the original data
along with associated metadata and provide appropriate convenience functions to
enable data analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute while the metadata is stored 
in the \texttt{meta} attribute. (Curently, \texttt{LightCurve} does 
not support the \texttt{meta} attribute.) It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, arrays or time ranges.  In order 
to provide instrument-specific specialisation, all the core SunPy data types 
support subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the SDO/AIA instrument. 
Data visualisation is provided by two functions: \texttt{peek()}, for quick 
plotting, and \texttt{plot()}, for plotting with more fine-grained control that 
integrates with \texttt{matplotlib}.

### 2014-01-29 4-Util.tex
Made astropy references consistent
repaired i.e. and e.g.

\subsection{World Coordinate System (WCS) Coordinates}\label{ssec:util:wcs}
Coordinate transformations are frequently a necessary task within the solar 
data analysis workflow. Likely the most often used transformation is from 
observer coordinates (e.g. sky coordinates) to a coordinate system which is 
mapped onto the solar surface (e.g. latitude and longitude). This 
transformation is necessary to compare the true physical distance between 
different solar features. This type of transformation is not unique
to solar observations, but is not often considered by astronomical packages
such as the Astropy 
coordinates package. The \verb|wcs| package in SunPy implements the World Coordinate 
System (WCS) for solar coordinates as described by \cite{Thompson2000}. The 
transformations currently implemented are those most useful 
for most solar data analysis, namely converting from Helioprojective-Cartesian 
(HPC) to Heliographic (HG) coordinates. HPC describes the positions on 
the Sun as angles measured from the center of the solar disk (usually in 
arcseconds) using cartesian coordinates (X, Y). This is the coordinate system 
most often defined in solar imaging data (see for example, images from 
\textit{SDO/AIA}, \textit{SOHO/EIT}, and \textit{TRACE}). 
HG coordinates express positions on the Sun using longitude and latitude on 
the solar sphere. There are two standards for this coordinate system, 
Stonyhurst-Heliographic where the origin is at the intersection of the solar 
equator and the central meridian as seen from Earth and 
Carrington-Heliographic is a system which is fixed to the Sun and does not depend on Earth. The 
implementation of these transformations pass through a common coordinate system 
called Heliocentric-Cartesian (HCC) where positions are expressed in true 
(deprojected) physical distances instead of angles on the celestial sphere.
These transformations require some knowledge of the location of the observer 
which is usually provided by the image header. In the case where it is 
not, the observer is assumed to be at Earth. Listing \ref{code:wcs_code} shows 
some examples of coordinate transforms carried out in SunPy using the 
\verb|wcs| utilities.

@@

\subsubsection{Sun}\label{ssec:util:sun}
The purpose of this module is to provide solar-specific data, for example ephemerides and
solar constants. The main namespace contains a number of functions which provide solar
ephemerides such as the Sun to Earth distance, solar cycle number, the mean 
anomaly, etc.
All of these functions take a time as their input which can be provided in any 
\texttt{parse\_time}
compatible format. 
A future version of SunPy will integrate with the AstroPy coordinates package and will 
likely make use of an ephemeris package.

\subsubsection{constants}\label{ssec:util:const}
The purpose of the constants package is to provide a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values both within the SunPy code base but also to the user. Every solar 
constant is provided as a Constant object as defined by Astropy. Each 
Constant object defines a Quantity, a number associated with a unit, along with 
the constant's provenance (i.e. reference) as well as its uncertainty. Using 
Astropy's Quantities, any solar constant can easily be converted between 
different units as can be seen in Listing~\ref{code:constants_code} as well
as between the SI or cgs unit systems with a single command.  As these objects inherit from 
Numpy's \texttt{ndarray}, they work well with standard representations of numbers.
For convenience a number of shortcuts to frequently used constants are provided 
directly when importing the sub-package. A larger list of constants can be 
accessed through an interface modelled on that provided by the SciPy constants 
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly a \texttt{print\_all()} function is available.

>>>>

\subsection{World Coordinate System (WCS) Coordinates}\label{ssec:util:wcs}
Coordinate transformations are frequently a necessary task within the solar 
data analysis workflow. Likely the most often used transformation is from 
observer coordinates (e.g., sky coordinates) to a coordinate system which is 
mapped onto the solar surface (e.g., latitude and longitude). This 
transformation is necessary to compare the true physical distance between 
different solar features. This type of transformation is not unique
to solar observations, but is not often considered by astronomical packages
such as the Astropy 
coordinates package. The \verb|wcs| package in SunPy implements the World Coordinate 
System (WCS) for solar coordinates as described by \cite{Thompson2000}. The 
transformations currently implemented are those most useful 
for most solar data analysis, namely converting from Helioprojective-Cartesian 
(HPC) to Heliographic (HG) coordinates. HPC describes the positions on 
the Sun as angles measured from the center of the solar disk (usually in 
arcseconds) using cartesian coordinates (X, Y). This is the coordinate system 
most often defined in solar imaging data (see for example, images from 
\textit{SDO/AIA}, \textit{SOHO/EIT}, and \textit{TRACE}). 
HG coordinates express positions on the Sun using longitude and latitude on 
the solar sphere. There are two standards for this coordinate system, 
Stonyhurst-Heliographic where the origin is at the intersection of the solar 
equator and the central meridian as seen from Earth and 
Carrington-Heliographic is a system which is fixed to the Sun and does not depend on Earth. The 
implementation of these transformations pass through a common coordinate system 
called Heliocentric-Cartesian (HCC) where positions are expressed in true 
(deprojected) physical distances instead of angles on the celestial sphere.
These transformations require some knowledge of the location of the observer 
which is usually provided by the image header. In the case where it is 
not, the observer is assumed to be at Earth. Listing \ref{code:wcs_code} shows 
some examples of coordinate transforms carried out in SunPy using the 
\verb|wcs| utilities.

@@

\subsubsection{Sun}\label{ssec:util:sun}
The purpose of this module is to provide solar-specific data, for example ephemerides and
solar constants. The main namespace contains a number of functions which provide solar
ephemerides such as the Sun to Earth distance, solar cycle number, the mean 
anomaly, etc.
All of these functions take a time as their input which can be provided in any 
\texttt{parse\_time}
compatible format. 
A future version of SunPy will integrate with the Astropy coordinates package and will 
likely make use of an ephemeris package.

\subsubsection{constants}\label{ssec:util:const}
The purpose of the constants package is to provide a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values both within the SunPy code base but also to the user. Every solar 
constant is provided as a Constant object as defined by Astropy. Each 
Constant object defines a Quantity, a number associated with a unit, along with 
the constant's provenance (i.e., reference) as well as its uncertainty. Using 
Astropy's Quantities, any solar constant can easily be converted between 
different units as can be seen in Listing~\ref{code:constants_code} as well
as between the SI or cgs unit systems with a single command.  As these objects inherit from 
Numpy's \texttt{ndarray}, they work well with standard representations of numbers.
For convenience a number of shortcuts to frequently used constants are provided 
directly when importing the sub-package. A larger list of constants can be 
accessed through an interface modelled on that provided by the SciPy constants 
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly a \texttt{print\_all()} function is available.
